Scarid behavior GAM/GAMMS

### 2018-11-28 r/Models.Rmd
11/27 more

library(startR)
library(here)
library(tidyverse)
library(mgcv)
library(car)
library(ggfortify)

@@

*need to add interaction terms*
```{r}
gamm1 <- gamm(fr ~ species_code + phase + s(length_cm) + s(pc1_bent) + s(pc2_bent) + s(scar_bm) +
                s(length_cm, by = as.numeric(species_code == "qup")) +
                s(pc1_bent, by = as.numeric(species_code == "qup")) +
                s(scar_bm, by = as.numeric(species_code == "qup")), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           weights = varIdent(form =~ 1 | species),
           data = m_data
           )
summary(gamm1$gam)
plot(gamm1$gam,pages=1)
plot(gamm1$lme) # shows heteroskedasticity
AIC(gamm1$lme)
```

@@

>>>>

library(startR)
library(here)
library(tidyverse)
library(mgcv)
library(car)
library(ggfortify)
library(xtable)
library(itsadug)

@@

*need to add interaction terms*
```{r}
# gamm1 <- gamm(fr ~ species_code + phase + s(length_cm) + s(pc1_bent) + s(pc2_bent) + s(scar_bm) +
#                 s(length_cm, by = as.numeric(species_code == "qup")) +
#                 s(pc1_bent, by = as.numeric(species_code == "qup")) +
#                 s(scar_bm, by = as.numeric(species_code == "qup")), 
#            family = gaussian(link=identity),
#            random = list(island=~1),
#            method = "REML",
#            weights = varIdent(form =~ 1 | species),
#            data = m_data
#            )
# summary(gamm1$gam)
# plot(gamm1$gam,pages=1)
# plot(gamm1$lme) # shows heteroskedasticity
# AIC(gamm1$lme)
```

@@

gamtabs(gamm4, type="HTML")
```
